---
title: "Group_27_ucsb_grad"
author: "Sarah Rohlfing and Mia Guarnieri"
date: "11/15/2021"
output: html_document
---
### Overview: 
In this report, we create a visualization to better observe the percentage of graduate students of different ethnicities enrolled at UCSB from 2008 to 2019. Data was sourced from the UCSB Office of Budget and Planning. 

```{r setup, include=FALSE, messages = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(here)
library(tidyverse)
library(calecopal)
```

```{r}
grad_ucsb <- read_csv(here("data", "ucsb_grad_data.csv"))
```

### Visualizing annual domestic graduate enrollment at UCSB

This basic column graph depicts the annual domestic graduate enrollment at UCSB from 2008-2019, color coded by student ethnicity.

```{r}
# Creating a basic column graph 
ggplot(data = grad_ucsb, aes(x = year_abbr, y = domestic_enrollment)) +
  geom_col(aes(fill = ethnicity), position = "fill") + # added position = fill to change the bars from absolute counts to proportions
  scale_fill_manual(values = cal_palette(name = "kelp1", n = 10, type = "continuous")) + #adding palette
  labs(x = "Year",
       y = "Percent Domestic Enrollment", 
       title = "Domestic Graduate Enrollment Percentages ") + # added labels, title
  theme_minimal() #setting the theme to minimal
```

**Figure 1:** Annual UCSB graduate enrollment percentages by ethnicity 2008-2019. Data: UCSB Office of Budget and Planning.

### Takeaway

The majority of the UCSB graduate student body is white, followed distantly by Asian/Pacific Islander, East Indian/Pakistani, and "Other" students. The university should consider implementing additional diversity, equity, and inclusion initiatives to promote increased diversity of the graduate student body and a more equitable distribution of enrolled students.

### Citation
"Campus Profiles".UCSB Office of Budget and Planning.https://bap.ucsb.edu/institutional-research/campus-profiles 